\documentclass{article}
\usepackage[dvipsnames]{xcolor}
\usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontawesome} % Add this line for FontAwesome icons
\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{Manuka Rahul \\}
\normalsize street, town, Hyderabad, 500001\\
\faEnvelope \  \href{mailto:rahulgmail.com}{rahul@gmail.com} $\mid$  
\faLinkedin~ \href{https://www.linkedin.com}{linkedin.com/in/rahul} $\mid$  
\faGithub~ \href{https://github.com/rahulpinto19/}{github.com/rahulpinto} $\mid$  
\faPhone \ +91-12345678 \\  
\hrulefill
{\\}
\end{center}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{SKILLS}} \\

\noindent\textbf{Languages}: C, C++, Java, Python, JavaScript\\
\textbf{Frameworks and Database}: MySQL, MongoDB, Express, ReactJS, Node.js, Redux \\
\textbf{Tools and Technologies}: OOPS, Data Structures, Git, Visual Studio Code, RESTful API, NPM, Websockets\\
\textbf{Others}: Chrome extensions, GitHub Actions, Firebase, Webpack services, Debugging, Code reviews\\
\\
\noindent \textbf{\underline{Expereince}} \\
\textbf{Google} \hfill Banglore,Karnataka \\
\textbf{Software Application Development Apprentice} \hfill April 2025 -Present 
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item Managed core GCP infrastructure components.
\item Optimized performance/cost on Google Cloud.
\item Supported/Automated tasks using GCP services.\\
\end{itemize}
\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT WORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{PERSONAL PROJECTS}} \\

\noindent \textbf{Project Name: Project1} \hfill \href{https://github.com/rahulpinto19/Vconnect}{\textcolor{blue}{link}} 
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
 \item write your project description in this fromat  
    \item use this to  keep \textbf{bold} letters
   \\
   
\end{itemize}

\noindent \textbf{Project Name: project2} \hfill \href{https://github.com/rahulpinto19/NewsApp}{\textcolor{blue}{link}}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
 \item write your project description in this fromat  
    \item use this to  keep \textbf{bold} letters
   \\
   
\end{itemize}

\noindent \textbf{Project Name: project3} \hfill \href{https://https://github.com/rahulpinto19/MachineLearning/tree/master/Breast%20Cancer%20Prediction/}{\textcolor{blue}{link}}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item write your project description in this fromat  
    \item use this to  keep \textbf{bold} letters
   \\
   
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{EDUCATION}} \\
{\\}
\textbf{Central University } \hfill  Haryana \\
\textit{Master of Computer Application} \hfill ~~~~~GPA: 7.2 \hfill June 2024 \\ \\
\textbf{Degree College} \hfill Hyderabad, Telangana \\
\textit{B.Sc. (Maths, Statistics, and Computers)} \hfill GPA: 7.7 \hfill February 2022 \\ \\
\textbf{New Era Jr. College} \hfill Hyderabad, Telangana \\
\textit{10+2 (Maths, Economics, Commerce)} \hfill GPA: 7.3 \hfill April 2018 \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ACHIEVEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{Achievements}} \\
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item Ranked \textbf{1st} in DSA among \textbf{500} students on the GeeksforGeeks platform (\href{https://www.geeksforgeeks.org/user/rahulyada9obo/}{\textcolor{blue}{link}}) in C++.
\item Coordinated and instructed the university coding club, delivering a comprehensive data structures curriculum in Java and C++ to \textbf{50} students.
\item Taught Mern Stack and Data structures, helping \textbf{20+} students master programming concepts.
\item Actively engaged as a content creator on YouTube, focusing on web development and DSA topics. (\href{https://www.youtube.com/@UNQCODER/}{\textcolor{blue}{youtube}})
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STRENGTHS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{Strengths}} \\
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item Excellent at analyzing complex problems and creating efficient, high-quality software solutions.
\item Skilled in HTML, CSS, JavaScript, and familiar with the React framework.
\item Quick to learn and adapt to new technologies and frameworks, always staying updated with industry trends.
\end{itemize}

\end{document}
